---
title: "My first project"
description: |
  The purpose of that project is to visualize operations on three coloured [<span class="R"> R </span>, <span class="G"> G </span>, <span class="B"> B </span>] light beam. We'll start with the simple ones like filtration or fluorescence and then move on to the more advanced ones.
author:
  - name: Piotr Migdał 
    url: https://p.migdal.pl
  - name: Szymon Błazucki
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='asis', echo=FALSE, message=FALSE}
cat(
  "<script src='https://cdn.jsdelivr.net/npm/vue'></script>",
  "<script src='https://unpkg.com/quantum-tensors'></script>",
  "<script src='https://unpkg.com/bra-ket-vue'></script>"
)
```


### Filtration

So at the beginning let's start with the simplest one - filtration. If we consider our light beam as a 3-dimensional vector where each dimension represents one component we can describe every operation as multiplying our vector by a matrix. For a blue light filter we have: 

$$ \begin{bmatrix}
R\\
G\\
B
\end{bmatrix} \begin{bmatrix}
1 & 0 & 0\\
0 & 1 & 0\\
0 & 0 & 0
\end{bmatrix} = \begin{bmatrix} R\\ G\\0 \end{bmatrix}
$$
It's completely ok to write it like this, but that's not intuitive for everyone. Especially if you are not familiar with linear algebra. To make it easier and more straightforward let's draw a matrix not as a set of 0 and 1 but as a table with circles inside it. Colour of each circle represents the component which it affects. Take a look on the following examples 

$$ \begin{bmatrix}
R\\
G\\
B
\end{bmatrix}\rightarrow \begin{bmatrix} R\\ G\\0 \end{bmatrix}
$$

<div id='opFiltr'></div>

<div id='ketviewFiltr'></div>


### Fluorescence
$$ \begin{bmatrix}
R\\
G\\
B
\end{bmatrix} \rightarrow \begin{bmatrix} R+G+B\\ 0\\0 \end{bmatrix}
$$
<div id='opFluR'></div>

### Another type of fluorescence
$$ \begin{bmatrix}
R\\
G\\
B
\end{bmatrix} \rightarrow \begin{bmatrix} 0\\ G+B\\0 \end{bmatrix}
$$
<div id='opFluGkillR'></div>



```{js, results='asis', echo=FALSE, message=FALSE}
const { Elements, Vector, Operator, Dimension, Cx } = QuantumTensors;
const { ComplexLegend, MatrixViewer, KetViewer } = BraKetVue;
const colorDim = new Dimension('colour', 3, ['R', 'G', 'B'])

const opFiltr = Operator.fromSparseCoordNames([
  ['0', '0', Cx(1)],
  ['1', '1', Cx(1)],
], [Dimension.position(3, 'color')]);

const opFluR = Operator.fromSparseCoordNames([
  ['0', '0', Cx(1)],
  ['0', '1', Cx(1)],
  ['0', '2', Cx(1)],
], [Dimension.position(3, 'color')]);

const opFluGkillR = Operator.fromSparseCoordNames([
  ['1', '1', Cx(1)],
  ['1', '2', Cx(1)],
], [Dimension.position(3, 'color')]);

new Vue({
  el: "#opFiltr",
  template: "<matrix-viewer :operator-raw='opFiltr' :dark-mode='false' :show-legend='false' />",
  components: {
    MatrixViewer
  },
  data() {
  	return {
    	opFiltr
		}
  }
})
new Vue({
  el: "#opFluR",
  template: "<matrix-viewer :operator-raw='opFluR' :dark-mode='false' :show-legend='false' />",
  components: {
    MatrixViewer
  },
  data() {
  	return {
    	opFluR
		}
  }
})

new Vue({
  el: "#opFluGkillR",
  template: "<matrix-viewer :operator-raw='opFluGkillR' :dark-mode='false' :show-legend='false' />",
  components: {
    MatrixViewer
  },
  data() {
  	return {
    	opFluGkillR
		}
  }
})

const ketviewFilter = Vector.fromSparseCoordNames(
  [["R", Cx(1/3)], ["G", Cx(1/3)], ["B", Cx(0)]],
  [colorDim]
);
const ketviewFluR = Vector.fromSparseCoordNames(
  [["R", Cx(1)], ["G", Cx(0)], ["B", Cx(0)]],
  [colorDim]
);
const ketviewFluGkillR = Vector.fromSparseCoordNames(
  [["R", Cx(0)], ["G", Cx(2/3)], ["B", Cx(0)]],
  [colorDim]
);

new Vue({
  el: "#ketviewFiltr",
  template: "<ket-viewer :operator-raw='ketviewFilter' :dark-mode='false' :show-legend='false' />", 
  components: {
    KetViewer
  },
  data() {
  	return {
    	ketviewFilter
		}
  }
})

```






```{css, echo=FALSE}
.R {
  color: red;
}
.G {
  color: green;
}
.B {
  color: blue;
}
```